---
title: "tidytime: tidy time series objects"
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# tidytime

Functions for tidying time series objects. `tidytime` can tidy `ts`, `xts` and `zoo` objects. The `zoo` tidier is identical to that available in the [broom][1] package, except that it returns a `dplyr::tbl_df`.

[1]: https://github.com/dgrtwo/broom/

All tidied time series have the following columns:

   - `index`: time value from the messy data. Can be `dbl`, `date` or `time`.
   - `series`: column with a descriptor for the type of messy data.
   - `value`: values from the original time series.

## Install

    > devtools::install_github('jayhesselberth/tidytime')

## Usage

### load

```{r load}
library(tidytime)
```

### time series (`ts`) objects

```{r time_series}
sample.ts <- ts(1:10, frequency = 4, start = c(1959, 2))

tidytime(sample.ts)
```

### `xts` objects

```{r xts, message = FALSE}
library(xts)
data(sample_matrix)
sample.xts <- as.xts(sample_matrix, descr='my new xts object')

tidytime(sample.xts)
```

### `zoo` objects

```{r zoo}
library(zoo)
x.Date <- as.Date("2003-02-01") + c(1, 3, 7, 9, 14) - 1
x <- zoo(rnorm(5), x.Date)

tidytime(x)
```
